---
title: Reproducing the analyses in the paper
output: github_document
---


Due to copyright reasons, we cannot bundle the full text of New York Times, Süddeutsche Zeitung and Le Fegaro news articles in this package.

However, a processed version of the corpus and dfm is available. The data was generated using the following code.

```{r, eval = FALSE}
require(rectr)
require(tibble)
require(dplyr)
require(quanteda)
paris <- readRDS("~/dev/infocrap/final_data_endefr.RDS") %>% mutate(content = paste(lede, content), lang = tolower(lang), id = row_number()) %>% select(content, lang, pubdate, headline, id)
```

```{r, eval = FALSE}
get_ft("fr")
get_ft("de")
get_ft("en")
```

```{r, eval = FALSE}
emb <- read_ft(c("fr", "de", "en"))
paris_corpus <- create_corpus(paris$content, paris$lang)
paris_dfm <- transform_dfm_boe(paris_corpus, emb)
docvars(paris_corpus, "headline") <- paris$headline
docvars(paris_corpus, "pubdate") <- paris$pubdate
docvars(paris_corpus, "id") <- paris$id

## Delete all text content, sorry, researchers!
paris_corpus[1:3391] <- NA
usethis::use_data(paris_corpus, overwrite = TRUE)
usethis::use_data(paris_dfm, overwrite = TRUE)
```

# Actual reproduction

Reproduce the analysis in the paper.

```{r}
require(rectr)
require(tidyverse)
require(quanteda)
paris_corpus
```

```{r}
paris_dfm
```

```{r}
emb <- read_ft(c("fr", "de", "en"))
paris_dfm_filtered <- filter_dfm(paris_dfm, paris_corpus, k = 5)
paris_dfm_filtered
```

```{r}
paris_gmm <- calculate_gmm(paris_dfm_filtered, seed = 42)
paris_gmm
```

## Appendix I

```{r}
get_sample <- function(i, paris_corpus, theta, threshold = 0.8, replace = FALSE) {
    tibble(hl = docvars(paris_corpus, "headline"), lang = docvars(paris_corpus, "lang"), prob = theta[,i]) %>% group_by(lang) %>% filter(prob > threshold) %>% sample_n(size = 5, weight = prob, replace = replace) %>% select(hl, lang, prob) %>% ungroup %>% arrange(lang, prob) %>% mutate(topic = i)
}

set.seed(42)
map_dfr(1:5, get_sample, paris_corpus, theta = paris_gmm$theta) %>% print(n = 100)
```

# tSTM

Again, due to copyright reasons, we cannot provide the full text. However, the DTM (in STM) format is available. It was created using this code.

```{r, eval = FALSE}
require(tidyverse)
require(googleLanguageR)
require(stm)
require(quanteda)

textdata <- readRDS("~/dev/infocrap/final_data_endefr.RDS") %>% mutate(content = paste(lede, content), lang = tolower(lang), id = row_number()) %>% select(content, lang, pubdate, headline, id)

## Please insert your google token here. Uncomment if needed.
## gl_auth("____.json")


textdata %>% filter(lang == "fr") %>% pull(content) -> FR_CONTENT
textdata %>% filter(lang == "de") %>% pull(content) -> DE_CONTENT
textdata %>% filter(lang == "en") %>% pull(content) -> EN_CONTENT
FR_DFM <- dfm(FR_CONTENT, remove = stopwords("fr"), remove_numbers = TRUE, remove_punct = TRUE) %>% dfm_trim(min_docfreq = 2)

FR_terms <- colnames(FR_DFM)


## Uncomment the following 3 lines if you want to do the google translation

## FR_trans_terms <- gl_translate(FR_terms, source = "fr")
## saveRDS(FR_trans_terms, "~/dev/infocrap/FR_trans_terms.RDS")
## saveRDS(FR_terms, "~/dev/infocrap/FR_terms.RDS")


DE_DFM <- dfm(DE_CONTENT, remove = stopwords("de"), , remove_numbers = TRUE, remove_punct = TRUE) %>% dfm_trim(min_docfreq = 2)

DE_terms <- colnames(DE_DFM)

## Uncomment the following 3 lines if you want to do the google translation

## DE_trans_terms <- gl_translate(DE_terms, source = "de")
## saveRDS(DE_trans_terms, "~/dev/infocrap/DE_trans_terms.RDS")
## saveRDS(DE_terms, "~/dev/infocrap/DE_terms.RDS")

DE_trans_terms <- readRDS("~/dev/infocrap/DE_trans_terms.RDS")
FR_trans_terms <- readRDS("~/dev/infocrap/FR_trans_terms.RDS")


FR_tokens <- tokens(FR_CONTENT, remove_numbers = TRUE, remove_punct = TRUE)

DE_tokens <- tokens(DE_CONTENT, remove_numbers = TRUE, remove_punct = TRUE)


recon <- function(token_obj, trans_terms) {
    tibble(text = tolower(token_obj)) %>% left_join(trans_terms, by = 'text') %>% filter(!is.na(translatedText)) %>% pull(translatedText) %>% paste(collapse = " ")
}

FR_recon_en_text <- map_chr(FR_tokens, recon, trans_terms = FR_trans_terms)

DE_recon_en_text <- map_chr(DE_tokens, recon, trans_terms = DE_trans_terms)

recon_complete_text <- c(FR_recon_en_text, EN_CONTENT, DE_recon_en_text)
textdata$translated_text <- recon_complete_text

min_docfreq <- (nrow(textdata) * 0.005) %>% ceiling
max_docfreq <- (nrow(textdata) * 0.99) %>% ceiling

dfm(textdata$translated_text, tolower = TRUE, stem = TRUE, remove = stopwords("en"), remove_number = TRUE, remove_punct = TRUE) %>% dfm_trim(min_docfreq = min_docfreq, max_docfreq = max_docfreq) %>% convert(to = 'stm') -> paris_translated_dfm
usethis::use_data(paris_translated_dfm, overwrite = TRUE)
```

```{r}
require(stm)
require(tidyverse)
require(googleLanguageR)
require(quanteda)

set.seed(42)
translated_stm  <- stm(translated_dfm$documents, translated_dfm$vocab, K = 5)
set.seed(42)
### Many duplicated
map_dfr(1:5, get_sample, paris_corpus, theta = translated_stm$theta, replace = TRUE) %>% print(n = 100)
```

```{r}
sessionInfo()
```
